% !TeX root = ../main.tex
\documentclass[../main.tex]{subfiles}
\begin{document}

\subsection{PhD courses}

27.5 to 30 ECTS have to be accumulated during the PhD.

Courses propositions:
\begin{itemize}
    \item \href{https://kurser.dtu.dk/course/41392}{41392 Journal club in fluid mechanics, 5 ETCS}. Responsible: Jens Honore Walther , Lyngby Campus, Building 403, Ph. (+45) 4525 4327 , jhwa@dtu.dk. Co-responsable: 	Knud Erik Meyer , Lyngby Campus, Building 403, Ph. (+45) 4525 4337 , keme@dtu.dk
    \item \href{https://kurser.dtu.dk/course/41690}{41690 Electron Microscopy and Analysis for Materials Research, 5 ECTS}. Responsible: 	Oleg Mishin , Lyngby Campus, Building 425, Ph. (+45) 4525 2267 , olmi@dtu.dk. Co-responsible: 	Jakob Birkedal Wagner , Lyngby Campus, Building 307, Ph. (+45) 4525 6471 , jabw@dtu.dk
    \item \href{https://kurser.dtu.dk/course/41691}{41691 Ph.D. course on application of x-ray diffraction in materials science, 5 ECTS}. Responsible: 	Wolfgang Pantleon , Lyngby Campus, Building 425, Ph. (+45) 4525 2315 , pawo@dtu.dk. Co-responsible	Karen Pantleon , Lyngby Campus, Building 425, Ph. (+45) 4525 2207 , kapa@dtu.dk
    \item \href{https://kurser.dtu.dk/course/41735}{41735 Experimental methods in 3D printing (additive manufacturing), 5 ECTS}. Responsible: 		Venkata Karthik Nadimpalli , Lyngby Campus, Building 427, Ph. (+45) 4525 4753 , vkna@dtu.dk. Co-responsible: David Bue Pedersen , Lyngby Campus, Building 427, Ph. (+45) 4525 4810 , dbpe@dtu.dk. From 3rd to 21st of August 2026.
    \item \href{https://employeecourses.dtu.dk/en/hr/administrative-staff/how-to-write-a-scientific-paper-2/}{How to write a scientific paper, 2.5 ECTS}. Teacher: Stuart Wright, AIS Sprog.
    \item \href{https://app.researchplanner.net/RP/index.cfm?PortalId=16596}{PhD-Planner: Supervision and facilitation of learning course} (1 ECTS). Email: liv@nordicwritingacademy.dk
    \textcolor{red}{still planning the spring of 2027, but the plan is to offer 4 courses, spread throughout the spring. Our deadline for announcing is September 1. So please feel free to contact us at that time if the dates have not been published at the homepage.}
    \item \href{https://kurser.dtu.dk/course/2026-2027/12950}{Sustainability evaluation and communication} (2.5 ETCS). Email: alau@dtu.dk \textcolor{red}{registration open 10th of August 2026}
\end{itemize}





\end{document}